---
title: "Case Study 3 Interim Report"
author: "Ekim Buyuk"
date: "10/1/2018"
output: html_document
---

Interim report 1: create an engaging visualization of observed infant mortality rates by year, county and race

```{r, include=FALSE}
#Libraries
if (!require("readr")) install.packages("readr")
library(readr)
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
if (!require("maps")) install.packages("maps")
library(maps)
if (!require("ggthemes")) install.packages("ggthemes")
library(ggthemes)
if (!require("mapproj")) install.packages("mapproj")
library(mapproj)
```


```{r}
#Loading and Visualizing Data
data <- read_csv("Yr1116Death.csv")

data %>% group_by(year) %>% summarise(count_n = n())

data %>% group_by(race) %>% summarise(count_n = n())

data %>% group_by(hisp) %>% summarise(count_n = n())

data %>% group_by(cores) %>% summarise(count_n = n())
```

Potential Visualizations:
1. Can we figure out where all of these counties are located and show a heat map of deaths?
2. A similar visualization to what we made that changes over years. As years progress, shows changes in deaths of races? How should we show counties? 

#Create a Dataframe with Simulated Data
```{r}
library(ggplot2)
nc_map <- tbl_df(map_data("county", region = "north carolina"))
# Simulate data to plot by county
data_frame(
  subregion = unique(nc_map$subregion),
  simdata = sample(50:500, length(unique(nc_map$subregion)))
) -> simdata_df
```

#Plot a Map

```{r}
nc_map <- left_join(nc_map, simdata_df)
ggplot() +
  geom_polygon(data=nc_map, color="black",
               aes(x=long, y=lat, group=subregion, fill=simdata)) +
  viridis::scale_fill_viridis(name="Simulated Data ", direction=-1) +
  coord_map("polyconic") +
  ggthemes::theme_map() +
  theme(legend.position="bottom")
```

