---
title: "Case Study 3 Interim Report"
author: "Ekim Buyuk"
date: "10/1/2018"
output: html_document
---

Interim report 1: create an engaging visualization of observed infant mortality rates by year, county and race

```{r, include=FALSE}
#Libraries
if (!require("readr")) install.packages("readr")
library(readr)
if (!require("readxl")) install.packages("readxl")
library(readxl)
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
if (!require("maps")) install.packages("maps")
library(maps)
if (!require("ggthemes")) install.packages("ggthemes")
library(ggthemes)
if (!require("mapproj")) install.packages("mapproj")
library(mapproj)
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
```


```{r}
#Loading and Merging Datasets
data <- read_csv("Yr1116Death.csv")
Country_Codes <- read_excel("Dataset Descriptions.xls", 
     sheet = "County Codes")

Country_Codes$CORES = as.integer(Country_Codes$CORES)
colnames(Country_Codes)[colnames(Country_Codes)=="CORES"] <- "cores"
merged_data<- left_join(Country_Codes,data)
write.csv(merged_data, "NC_Infant_Death_Merged.csv")

nc_map <- tbl_df(map_data("county", region = "north carolina"))
colnames(nc_map)[colnames(nc_map)=="subregion"] <- "COUNTY"
merged_data = merged_data %>% mutate(COUNTY = tolower(COUNTY))
nc_map_join <- left_join(nc_map,merged_data)
write.csv(nc_map_join, "NC_Infant_Death.csv")
```

Potential Visualizations:
1. Can we figure out where all of these counties are located and show a heat map of deaths?
2. A similar visualization to what we made that changes over years. As years progress, shows changes in deaths of races? How should we show counties? 

#Some EDA For No Reason

```{r}
Deaths_Per_County = nc_map_join %>% group_by(COUNTY) %>% summarise(count_n = n())

#data %>% group_by(race) %>% summarise(count_n = n())
#data %>% group_by(hisp) %>% summarise(count_n = n())
#data %>% group_by(cores) %>% summarise(count_n = n())
```

#Plot a Map

Not functioning properly...

```{r}
#Attempting to Plot a map on a gradient based on # of Deaths. Can we get labels on this map? 
ggplot() +
  geom_polygon(data=Deaths_Per_County, color="black",
               aes(x=long, y=lat, group=COUNTY, fill=count_n)) +
  viridis::scale_fill_viridis(name="Simulated Data ", direction=-1) +
  coord_map("polyconic") +
  ggthemes::theme_map() +
  theme(legend.position="bottom")
```

